Coherent optical association of a single molecule

### 2020-10-05 paper.tex
... remove notes
Update Fig 2 and 3 descriptions

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure*}[ht!]
  \includegraphics[height=4.5cm]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman resonance from atomic state $Na(2,2)\ Cs(3,3)$ to the first molecular bound state
    using a $0.1\mathrm{ms}$ pulse.
    The full width half maximum (FWHM) of $8.43(81) \mathrm{kHz}$ of the resonance
    is consistent with the FWHM for a coherent $0.1\mathrm{ms}$ $8.0 \mathrm{kHz}$ $\pi$ pulse.
    (D) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
    proving the coherence of the Raman transfer process.
    \label{f-raman}}
\end{figure*}

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning. (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state. When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
We observed the narrowest linewidth of $8.43(81) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.1 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.843(81)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $63\%$ of initial ground state atoms are transferred into the molecular state.

\begin{figure*}
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $84.9(49) \mathrm{\mu s}$
    measured from the Raman transition data.
    \label{f-lifetime}}
\end{figure*}

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B). The fit shows that we have a Raman Rabi frequency of $...$. The molecule we form has a lifetime of $84.9(49) \mathrm{\mu s}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

@@

(ASE filter)

@@

% ASE in caption for figure 4 and when mentioning the setup ahead of time
% figure 4

% ? SM?

>>>>

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure*}[ht!]
  \includegraphics[height=4.5cm]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman resonance from atomic state $Na(2,2)\ Cs(3,3)$ to the first molecular bound state
    using a $0.12\mathrm{ms}$ pulse.
    The full width half maximum (FWHM) of $7.56(82) \mathrm{kHz}$ of the resonance
    is consistent with the FWHM for a coherent $0.12\mathrm{ms}$ $\pi$ pulse $6.7 \mathrm{kHz}$.
    (D) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
    proving the coherence of the Raman transfer process.
    \label{f-raman}}
\end{figure*}

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning. (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state. When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.

\begin{figure*}
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.204(13) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    \label{f-lifetime}}
\end{figure*}

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B). The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) \mathrm{kHz}$. The molecule we form has a lifetime of $0.204(13) \mathrm{ms}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

@@

@@
